Learning From Massive Noisy Labeled Data for Image Classification

### 2015-04-06 paper.tex
Polish the subsection of dataset

Deep learning with massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2013panda}, scene classification~\cite{farabet2013learning}, etc. While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods require reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems. Thus it is necessary to develop new efficient labeling and training frameworks for deep learning.

@@

Our goal is to build an end-to-end deep learning system that is capable of training with both limited clean labels and massive noisy labels more effectively. Figure~\ref{fig:overview} shows the framework of our approach. We collect a million clothes images from E-commerce websites. Each image is automatically assigned a noisy label according to the keywords in its surrounding text. After that, we manually refine 72,000 image labels, which constitute a clean sub-dataset. All the data are then used to train CNNs, while the major challenge is to identify and correct the wrong labels during the training process.

@@

\subsection{Dataset} % (fold)
\label{sub:dataset}
We build a large-scale clothes dataset by crawling images and their surrounding texts from some online shopping websites. These surrounding texts are valuable, because they usually contain several keywords that can be further converted to visual tags. Specific to our task of clothes classification, we define $14$ classes: T-shirt, Shirt, Knitwear, Chiffon, Sweater, Coat, Windbreaker, Jacket, Down Coat, Suit, Shawl, Dress, Vest, and Underwear.

In order to learn a clothes classifier and evaluate its performance, we manually label a small part of all the images and split it into training ($\mathcal{D}_c$), validation and test sets. Meanwhile the remaining data construct the noisy labeled training dataset $\mathcal{D}_n$. A crucial data preprocessing step is to remove near duplicate images from $\mathcal{D}_c$ and $\mathcal{D}_n$, which ensures the reliability of our test protocol. The size of training datasets are $|\mathcal{D}_c| = 47570$ and $|\mathcal{D}_n| = 1.5M$, while validation and test set consist of 14,313 and 10,526 images respectively. The confusion matrix between clean and noisy labels are presented in Figure~\ref{fig:cm_strong_weak}. We can see that the overall accuracy is only $61.54\%$, which means that the labels converted from surrounding texts are quite noisy.

>>>>

Deep learning with massive amount of supervised training data has recently shown very impressive improvement on multiple image recognition challenges including image classification~\cite{krizhevsky2012imagenet}, attribute learning~\cite{zhang2013panda}, scene classification~\cite{farabet2013learning}, \etc. While state-of-the-art results have been continuously reported~\cite{zeiler2013visualizing,simonyan2014very,szegedy2014going}, all these methods require reliable annotations from millions of images~\cite{deng2009imagenet} which are often expensive and time-consuming to obtain~\cite{deng2009imagenet}, preventing deep models from being quickly trained on new image recognition problems. Thus it is necessary to develop new efficient labeling and training frameworks for deep learning.

@@

Our goal is to build an end-to-end deep learning system that is capable of training with both limited clean labels and massive noisy labels more effectively. Figure~\ref{fig:overview} shows the framework of our approach. We collect a million clothes images from E-commerce websites. Each image is automatically assigned a noisy label according to the keywords in its surrounding text. After that, we manually refine 72409 image labels, which constitute a clean sub-dataset. All the data are then used to train CNNs, while the major challenge is to identify and correct the wrong labels during the training process.

@@

\subsection{Dataset} % (fold)
\label{sub:dataset}
Since there is no publicly available dataset that has both clean and noisy labels, to test our method under real-world scenario, we build a large-scale clothing dataset by crawling images from some online shopping websites. More than a million images are collected together with their surrounding texts provided by the sellers. These surrounding texts usually contain rich information about the products, which can be further converted to visual tags. Specific to our task of clothing classification, we define $14$ class labels: T-shirt, Shirt, Knitwear, Chiffon, Sweater, Hoodie, Windbreaker, Jacket, Down Coat, Suit, Shawl, Dress, Vest, and Underwear. We assign an image a noisy label if we find its surrounding text contains only the keywords of that label, otherwise we discard the image to reduce ambiguity.

After that we manually refine the noisy labels of a small portion of all the images and split them into training ($\mathcal{D}_c$), validation and test sets. On the other hand, the remaining data construct the noisy labeled training dataset ($\mathcal{D}_n$). A crucial step here is to remove from $\mathcal{D}_c$ and $\mathcal{D}_n$ the images that are near duplicate with some image in the validation and test sets, which ensures the reliability of our test protocol. Finally, the size of training datasets are $|\mathcal{D}_c| = 47570$ and $|\mathcal{D}_n| = 10^6$, while validation and test set have 14313 and 10526 images, respectively.

The confusion matrix between clean and noisy labels is presented in Figure~\ref{fig:cm_strong_weak}. We can see that the overall accuracy is $61.54\%$, and some pairs of classes are very confusing with each other (\eg Knitwear and Sweater). This confusion matrix indicates that the noisy labels are not so reliable.

% We build a large-scale clothes dataset by crawling images and their surrounding texts from some online shopping websites. These surrounding texts are valuable, because they usually contain several keywords that can be further converted to visual tags. Specific to our task of clothes classification, we define $14$ classes: T-shirt, Shirt, Knitwear, Chiffon, Sweater, Coat, Windbreaker, Jacket, Down Coat, Suit, Shawl, Dress, Vest, and Underwear.

% In order to learn a clothes classifier and evaluate its performance, we manually label a small part of all the images and split it into training ($\mathcal{D}_c$), validation and test sets. Meanwhile the remaining data construct the noisy labeled training dataset $\mathcal{D}_n$. A crucial data preprocessing step is to remove near duplicate images from $\mathcal{D}_c$ and $\mathcal{D}_n$, which ensures the reliability of our test protocol. The size of training datasets are $|\mathcal{D}_c| = 47570$ and $|\mathcal{D}_n| = 1.5M$, while validation and test set consist of 14,313 and 10,526 images respectively. The confusion matrix between clean and noisy labels are presented in Figure~\ref{fig:cm_strong_weak}. We can see that the overall accuracy is only $61.54\%$, which means that the labels converted from surrounding texts are quite noisy.
